Multi-scale assessment of a grassland productivity model

### 2020-12-28 manuscript/supplement2.Rmd
add MAP scaling reference

The vegetaion parameter V corresponds to the fCover, which is mapped to PhenoCam G\textsubscript{cc} using the transfer function:

@@

## References
Richardson, A. D., Hufkens, K., Milliman, T., Aubrecht, D. M., Chen, M., Gray, J. M., … Frolking, S. (2018). Tracking vegetation phenology across diverse North American biomes using PhenoCam imagery. Scientific Data, 5(1), 180028. https://doi.org/10.1038/sdata.2018.28  
Hufkens, K., Keenan, T. F., Flanagan, L. B., Scott, R. L., Bernacchi, C. J., Joo, E., … Richardson, A. D. (2016). Productivity of North American grasslands is increased under future climate scenarios despite rising aridity. Nature Climate Change, 6(7), 710–714. https://doi.org/10.1038/nclimate2942

>>>>

The vegetaion parameter V corresponds to the fCover, which is mapped to PhenoCam G\textsubscript{cc} using the transfer function based on the relationship between annual precipitation and fractional vegetation cover (Donohue et al. 2013).:

@@

## References
Donohue, R. J., Roderick, M. L., McVicar, T. R., & Farquhar, G. D. (2013). Impact of CO 2 fertilization on maximum foliage cover across the globe’s warm, arid environments. Geophysical Research Letters, 40(12), 3031–3035. https://doi.org/10.1002/grl.50563  
Hufkens, K., Keenan, T. F., Flanagan, L. B., Scott, R. L., Bernacchi, C. J., Joo, E., … Richardson, A. D. (2016). Productivity of North American grasslands is increased under future climate scenarios despite rising aridity. Nature Climate Change, 6(7), 710–714. https://doi.org/10.1038/nclimate2942  
Richardson, A. D., Hufkens, K., Milliman, T., Aubrecht, D. M., Chen, M., Gray, J. M., … Frolking, S. (2018). Tracking vegetation phenology across diverse North American biomes using PhenoCam imagery. Scientific Data, 5(1), 180028. https://doi.org/10.1038/sdata.2018.28
